%-----------------------------------------------------------------------------------------------------------------------------------------------%
%	The MIT License (MIT)
%
%	Copyright (c) 2021 Jitin Nair
%
%	Permission is hereby granted, free of charge, to any person obtaining a copy
%	of this software and associated documentation files (the "Software"), to deal
%	in the Software without restriction, including without limitation the rights
%	to use, copy, modify, merge, publish, distribute, sublicense, and/or sell
%	copies of the Software, and to permit persons to whom the Software is
%	furnished to do so, subject to the following conditions:
%	
%	THE SOFTWARE IS PROVIDED "AS IS", WITHOUT WARRANTY OF ANY KIND, EXPRESS OR
%	IMPLIED, INCLUDING BUT NOT LIMITED TO THE WARRANTIES OF MERCHANTABILITY,
%	FITNESS FOR A PARTICULAR PURPOSE AND NONINFRINGEMENT. IN NO EVENT SHALL THE
%	AUTHORS OR COPYRIGHT HOLDERS BE LIABLE FOR ANY CLAIM, DAMAGES OR OTHER
%	LIABILITY, WHETHER IN AN ACTION OF CONTRACT, TORT OR OTHERWISE, ARISING FROM,
%	OUT OF OR IN CONNECTION WITH THE SOFTWARE OR THE USE OR OTHER DEALINGS IN
%	THE SOFTWARE.
%	
%
%-----------------------------------------------------------------------------------------------------------------------------------------------%

%----------------------------------------------------------------------------------------
%	DOCUMENT DEFINITION
%----------------------------------------------------------------------------------------

% article class because we want to fully customize the page and not use a cv template
\documentclass[a4paper,12pt]{article}

%----------------------------------------------------------------------------------------
%	FONT
%----------------------------------------------------------------------------------------

% % fontspec allows you to use TTF/OTF fonts directly
% \usepackage{fontspec}
% \defaultfontfeatures{Ligatures=TeX}

% % modified for ShareLaTeX use
% \setmainfont[
% SmallCapsFont = Fontin-SmallCaps.otf,
% BoldFont = Fontin-Bold.otf,
% ItalicFont = Fontin-Italic.otf
% ]
% {Fontin.otf}

%----------------------------------------------------------------------------------------
%	PACKAGES
%----------------------------------------------------------------------------------------
\usepackage{url}
\usepackage{parskip} 	

%other packages for formatting
\RequirePackage{color}
\RequirePackage{graphicx}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage[scale=0.9]{geometry}

%tabularx environment
\usepackage{tabularx}

%for lists within experience section
\usepackage{enumitem}

% centered version of 'X' col. type
\newcolumntype{C}{>{\centering\arraybackslash}X} 

%to prevent spillover of tabular into next pages
\usepackage{supertabular}
\usepackage{tabularx}
\newlength{\fullcollw}
\setlength{\fullcollw}{0.47\textwidth}

%custom \section
\usepackage{titlesec}				
\usepackage{multicol}
\usepackage{multirow}

%CV Sections inspired by: 
%http://stefano.italians.nl/archives/26
\titleformat{\section}{\Large\scshape\raggedright}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{10pt}{10pt}

%for publications
\usepackage[style=authoryear,sorting=ynt, maxbibnames=2]{biblatex}

%Setup hyperref package, and colours for links
\usepackage[unicode, draft=false]{hyperref}
\definecolor{linkcolour}{rgb}{0,0.2,0.6}
\hypersetup{colorlinks,breaklinks,urlcolor=linkcolour,linkcolor=linkcolour}
\addbibresource{citations.bib}
\setlength\bibitemsep{1em}

%for social icons
\usepackage{fontawesome5}

%debug page outer frames
%\usepackage{showframe}


% job listing environments
\newenvironment{jobshort}[2]
    {
    \begin{tabularx}{\linewidth}{@{}l X r@{}}
    \textbf{#1} & \hfill &  #2 \\[3.75pt]
    \end{tabularx}
    }
    {
    }

\newenvironment{joblong}[2]
    {
    \begin{tabularx}{\linewidth}{@{}l X r@{}}
    \textbf{#1} & \hfill &  #2 \\[3.75pt]
    \end{tabularx}
    \begin{minipage}[t]{\linewidth}
    \begin{itemize}[nosep,after=\strut, leftmargin=1em, itemsep=3pt,label=--]
    }
    {
    \end{itemize}
    \end{minipage}    
    }


% !TEX TS-program = xelatex
% !TEX encoding = UTF-8 Unicode
% -*- coding: UTF-8; -*-
% vim: set fenc=utf-8

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% SIMPLE-RESUME-CV
%% <https://github.com/zachscrivena/simple-resume-cv>
%% This is free and unencumbered software released into the
%% public domain; see <http://unlicense.org> for details.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% See "README.md" for instructions on compiling this document.

\documentclass[letterpaper,MMMyyyy,nonstopmode]{simpleresumecv}
% Class options:
% a4paper, letterpaper, nonstopmode, draftmode
% MMMyyyy, ddMMMyyyy, MMMMyyyy, ddMMMMyyyy, yyyyMMdd, yyyyMM, yyyy

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% PREAMBLE.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% CV Info (to be customized).
\newcommand{\CVAuthor}{Cathy Kaile Fang}
\newcommand{\CVTitle}{Cathy Fang_CV_2025}
\newcommand{\CVNote}{CV compiled on {\today}}
%\newcommand{\CVWebpage}{http://www.example.com/~johndoe}

% PDF settings and properties.
\hypersetup{
pdftitle={\CVTitle},
pdfauthor={\CVAuthor},
pdfsubject={\CVWebpage},
pdfcreator={XeLaTeX},
pdfproducer={},
pdfkeywords={},
unicode=true,
bookmarks=true,
bookmarksopen=true,
pdfstartview=FitH,
pdfpagelayout=OneColumn,
pdfpagemode=UseOutlines,
hidelinks,
breaklinks}

% Shorthand.
\newcommand{\Code}[1]{\mbox{\textbf{#1}}}
\newcommand{\CodeCommand}[1]{\mbox{\textbf{\textbackslash{#1}}}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% ACTUAL DOCUMENT.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%%%%%%%%%%%%%%%
% TITLE BLOCK %
%%%%%%%%%%%%%%%

\Title{\CVAuthor}

\begin{SubTitle}
%\href{https://www.google.com/maps/place/17+Prime+Avenue,+Springfield,+Pennsylvania+10111,+USA}
{Apt 4, 50 Rue de L'Église, Verdun, QC, Canada}
\par
\href{kaile.fang@mail.mcgill.ca}
{kaile.fang@mail.mcgill.ca}
\,\SubBulletSymbol\,
+1\,(902)\,541-0219
\,\SubBulletSymbol\,
\href{www.linkedin.com/in/kaile-fang-28a7a226b}
{www.linkedin.com/in/kaile-fang-28a7a226b}
%\href{\CVWebpage}
%{\url{\CVWebpage}}
\end{SubTitle}

\begin{Body}

%%%%%%%%%%%%%%%
%% EDUCATION %%
%%%%%%%%%%%%%%%

\Section
{Education}
{Education}
{PDF:Education}

\Entry
{\textbf{McGill University}},
Montreal, QC, Canada

\Gap

B.A. in Psychology, minor in statistics and behavioral sciences
\hfill
\DatestampYMD{2022}{08} ---
\DatestampYMD{2025}{12}

\SubBulletItem
Thesis:
Functional (Dys)connectivity and Cognition in Early Psychosis.
\SubBulletItem
\href{https://www.mcgill.ca/psychiatry/katie-lavigne}
{Supervisor:
Dr. Katie Lavigne}
\SubBulletItem
Focus:
Cognition, early psychosis, neuroimaging, multivariate distance matrix regression.


%%%%%%%%%%%%%%%%%%%%%%%%%
%% RESEARCH EXPERIENCE %%
%%%%%%%%%%%%%%%%%%%%%%%%%

\Section
{Work Experience}
{Work Experience}
{PDF:WorkExperience}

\Entry
\href{https://douglas.research.mcgill.ca/open-science-douglas/}
{\textbf{Douglas Research Centre}}, Verdun, QC, Canada


\BulletItem
Cerebral Imaging Centre (CIC) Seminar Facilitator
\hfill
\DatestampYMD{2024}{12} -- Present

Supervisor: Dr. Mallar Chakravarty (Director of CIC)
\begin{Detail}
\SubBulletItem
Speaker invite, arrange and host in person seminars, student lunches and meetings.
\SubBulletItem
Graphics design on Canva. 
\SubBulletItem
Video editing and YouTube uploads. 
\end{Detail}

\Gap
\BulletItem
Open Science Intern
\hfill
\DatestampYMD{2024}{05} -- \DatestampYMD{2025}{09}



Team:
Dr. Katie Lavigne (OS program lead) and
Dr. Isabel Bacellar (OS program coordinator)
\begin{Detail}
\SubBulletItem
Scholarly and Societal Impact of Open Science Practices: A Narrative Review.
\SubBulletItem
Open psychological measures.
\SubBulletItem
Resources and practical guides on Open Science practices for the Douglas website.
\SubBulletItem
Search funding opportunities and write funding applications.
\SubBulletItem
Identify Open Access articles of affiliated researchers.
\end{Detail}

\BigGap
\Entry
\textbf{Private English Tutor}
\hfill
\DatestampYMD{2023}{07} -- 
\DatestampYMD{2023}{03}

\Section
{Research}
{Research}
{PDF:Research}

{\textbf{Miocevic Lab (Dr. Milica Miocevic)}, McGill University}
\Gap
\BulletItem
PSYC 385, one semester research course
\hfill
\DatestampYMD{2025}{05} -- Present
\begin{Detail}
Develop a Shiny App in R for calculating empirical power of single case experimental design and a tutorial paper.
\end{Detail}

\BigGap
\href{https://www.crispdouglas.ca}
{\textbf{Lavigne Lab (Dr. Katie Lavigne)}, CRISP research group, Douglas Research Centre}
\Gap
\BulletItem
PSYC 484 D1/D2, one-year thesis project 
\hfill
\DatestampYMD{2024}{09} -- Present

\BulletItem
PSYC 499, reading project 
\hfill
\DatestampYMD{2024}{09} -- 
\DatestampYMD{2024}{12}

\begin{Detail}
Pre-registered narrative review on the impact of open science practices.
\end{Detail}
\BigGap
\textbf{OpenTransfer group}, FORRT (Framework for Open and Reproducible Research Training) and COSN (Chinese Open Science Network)

Translator
\hfill
\DatestampYMD{2024}{07} -- Present

\begin{Detail}
Translate FORRT Glossary of Open Science Terms into proficient Chinese. 
\SubBulletItem
Test and run 'AutoTrans' program.
\SubBulletItem
Compile translation results.
\SubBulletItem
Manual polishing and editing of results.
\end{Detail}

\BigGap
\textbf{Sladek Lab (Dr. Robert Sladek)}, Human Genetics, McGill University

Project assistant
\hfill
\DatestampYMD{2024}{04} -- 
\DatestampYMD{2024}{09}

\begin{Detail}
RNA Denervation project with Jeffrey Yu, M.sc. Student
\SubBulletItem
Exploratory and correlational analyses of genetic data in R. 
\SubBulletItem
Differential correlation analysis using discordant package. 
\end{Detail}

\BigGap
\textbf{MOGILab (Dr. Jeffrey Mogil)}, Department of Psychology, McGill University

Volunteer
\hfill
\DatestampYMD{2022}{12} -- Present

\BulletItem
“Pain + Opioid Withdrawal in Mice”, Hannah Derue, Ph.D. Candidate
\hfill
\DatestampYMD{2023}{08} -- Present

\begin{Detail}
\SubBulletItem
Algorithm training of DeepLabCut for labelling mouse body parts and automatic behavioural scoring of open field and tail suspension tests.
\SubBulletItem
Behavioral testing (operant boxes). 
\SubBulletItem
Data logging and analysis. 
\end{Detail}
\BulletItem
“Pain/Sick”, Laila Chaudry, Ph.D. candidate  
\hfill
\DatestampYMD{2023}{01} -- \DatestampYMD{2023}{06}

\begin{Detail}
\SubBulletItem
Human data collection, data logging and management. 
\SubBulletItem
SONA participant pool (research study participation sign-up platform) setup. 
\end{Detail}


\Section
{Public Engagement}
{Public Engagement}
{PDF:PublicEngagement}
\textbf{Tanenbaum Open Science Institute (TOSI)} Tainee Council, Montreal Neurological Institute (MNI), QC

\BulletItem
Journal Club Project Coordinator 
\hfill
\DatestampYMD{2023}{06} -- Present
\begin{Detail}
Organzie and host monthly OS/ReproducibiliTea journal club meetings.
\end{Detail}
\Gap
\BulletItem
Communications Director
\hfill
\DatestampYMD{2022}{10} -- 
\DatestampYMD{2023}{06}

\begin{Detail}
Event planning and outreach. 
\end{Detail}

\BigGap
\textbf{Douglas Open Science Trainee Council} 
\hfill
\DatestampYMD{2024}{07} -- Present

Monthly Douglas OS training series. 
\begin{Detail}
\BulletItem
Promote OS in the Douglas undergraduate community. 
\BulletItem
Speaker introduction, Zoom monitoring and lead Q+A sessions.
\end{Detail}
%%%%%%%%%%%%%%%%%%
%% PUBLICATIONS %%
%%%%%%%%%%%%%%%%%%

\Section
{Publications}
{Publications}
{PDF:Publications}

\SubSection
{In Progress}
{In Progress}
{PDF:InProgress}

% Declare a new group to limit the scope of \MaxNumberedItem to this subsection.
\begingroup
\renewcommand{\MaxNumberedItem}{[88]}

\Gap
\NumberedItem{[1]}
\href{https://doi.org/10.17605/OSF.IO/QPZF5}
{\underline{Fang, C.}, Bacellar, I., Lavgine, KM.
``Impact of Open Science Practices: A Narrative Review'', pre-registered on OSF.
}
\endgroup

\BigGap
\Section
{Presentations}
{Presentations}
{PDF:Presentations}
\begingroup
\renewcommand{\MaxNumberedItem}{[88]}
\SubSection
{Talks}
{Talks}
{PDF:Talks}
\Gap
\NumberedItem{[1]}
\href{https://scientistamcgill.wordpress.com/3-mt-presentations-2024/}
{Fang, C., Danyluik, M., Lavgine, KM.
\textit{Stay Connected: Insights into Cognitive Impairments in Early Psychosis} - 3MT 
at Scientista 3rd Annual Symposium: Science for Hope. \textbf{Runner up prize}.
\DatestampYM{2025}{03}.}

\Gap
\NumberedItem{[2]}
\href{https://www.cogsurf.org}
{Fang, C., Bacellar, I., Lavgine, KM.
\textit{Impact of Open Science Practices: A Narrative Review} - 3MT 
at CogSurf (Cognitive Science
Undergraduate Research Forum).
\DatestampYM{2025}{02}.}

\Gap
\NumberedItem{[3]}
{Fang, C., Bacellar, I., Lavgine, KM.
\textit{Impact of Open Science Practices: A Narrative Review}
at ReproducibiliTea Journal Club of Western Institute for Neuroscience. 
\DatestampYM{2025}{02}. [invited]}

\Gap
\NumberedItem{[4]}
{Fang, C., Bacellar, I., Lavgine, KM.
\textit{Impact of Open Science Practices: A Narrative Review}
in TOSI OS Journal Club.
\DatestampYM{2024}{11}.}

\SubSection
{Poster}
{Poster}
{PDF:Poster}
\Gap
\NumberedItem{[1]}
{Fang, C., Danyluik, M., Lavgine, KM.
\textit{Understanding Cognitive Impairment in Early Psychosis through Functional Brain Dysconnectivity: A Whole-Brain Analysis Approach} at Healthy Brains Healthy Lives Symposium 2025.
\DatestampYM{2025}{05}.}

\NumberedItem{[2]}
{Fang, C., Danyluik, M., Lavgine, KM.
\textit{Understanding Cognitive Impairment in Early Psychosis through Functional Brain Dysconnectivity: A Whole-Brain Analysis Approach} at Neuropsychology Day 2025.
\DatestampYM{2025}{02}.}

\NumberedItem{[2]}
{Fang, C., Danyluik, M., Lavgine, KM.
\textit{Understanding Cognitive Impairment in Early Psychosis through Functional Brain Dysconnectivity: A Whole-Brain Analysis Approach} at Undergraduate Science Showcase, McGill University.
\DatestampYM{2025}{03}.}

\NumberedItem{[3]}
{Fang, C., Bacellar, I., Lavgine, KM.
\textit{Impact of Open Science Practices: A Narrative Review} at the TOSI Open Science Research Fair.
\DatestampYM{2025}{02}.}

\Gap
\NumberedItem{[4]}
{Fang, C., Bacellar, I., Lavgine, KM.
\textit{Impact of Open Science Practices: A Narrative Review} at the Open Science in Action Symposium (MNI).
\DatestampYM{2024}{11}.}

\Gap
\NumberedItem{[5]}
{Fang, C., Bacellar, I., Lavgine, KM.
\textit{Impact of Open Science: A Review}
at the Undergrad Research Expo (Douglas Research Centre).
\DatestampYM{2024}{07}.}

\endgroup

%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% AWARDS & SCHOLARSHIPS %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%

\Section
{Awards \&\newline
Scholarships}
{Awards \& Scholarships}
{PDF:AwardsAndScholarships}

\href{https://openscienceofficehours.github.io/osoh_website/os-badges/}
{\textbf{Open Science Badge - Science Communication}}
\hfill
\DatestampY{2024}
\begin{Detail}
For organizing OS journal clubs and talks on OS.
\end{Detail}


\BigGap
\textbf{TOSI OS Helpers Program}

\Gap
\BulletItem
\href{https://www.mcgill.ca/neuro/jerome-fortin-phd}
{Barnett Lab (Dr. Alex Barnett)} at MNI
\hfill
\DatestampYMD{2025}{05} -- 
\DatestampYMD{2025}{07}

\begin{Detail}
\SubBulletItem
Create a Data Management Plan; Introduction to ORCiD, GitHub and McGill e-scholarship.
\end{Detail}

\BulletItem
\href{https://www.mcgill.ca/neuro/jerome-fortin-phd}
{Fortin Lab (Dr. Jerome Fortin)} at MNI
\hfill
\DatestampYMD{2025}{05} -- 
\DatestampYMD{2025}{07}

\begin{Detail}
\SubBulletItem
Create a Data Management Plan
\end{Detail}

\BulletItem
\href{https://sites.google.com/view/ruthazerlab/home}
{Ruthazer Lab (Dr. Edward Ruthazer)} at MNI
\hfill
\DatestampYMD{2024}{09} -- 
\DatestampYMD{2024}{11}

\begin{Detail}
\SubBulletItem
Create a Data Management Plan for an NIH grant application.
\SubBulletItem
Deposit articles to McGill e-scholarship as a means of self-archiving.
\SubBulletItem
Introduce ORCID (a persistent identifier for researchers) and open access.
\end{Detail}


%%%%%%%%%%%%%%%%%%%%%%%
%% CAMPUS ACTIVITIES %%
%%%%%%%%%%%%%%%%%%%%%%%

\Section
{Other}
{Other}
{PDF:Other}
\Entry
{\textbf{McGill Science Computer Task Force}}

Member
\hfill
\DatestampYMD{2024}{09} -- Present

\begin{Detail}
Hardware lending, printing services and general guidance on services offered.
\end{Detail}


\BigGap
\Entry
{\textbf{McGill Psychology Student Association}}

Mentor
\hfill
\DatestampYMD{2023}{09} -- Present
\begin{Detail}
Guide students on topics such as finding a research position, course selection and career paths.
\end{Detail}

\BigGap
\Entry
{\textbf{McGill International Students Network}}

Mentor, International Buddy Program
\hfill
\DatestampYMD{2023}{08} -- Present
\begin{Detail}
Guide students on living in McGill residence, life in Montreal and others.
\end{Detail}

\BigGap
\Entry
\href{https://www.toastmasters.org/}
{\textbf{Toastmasters International}}

Member, Datang Advanced Toastmasters Club
\hfill
\DatestampYMD{2023}{07} -- \DatestampYMD{2023}{09}

\begin{Detail}
Given 3 speeches and organized 1 table-topic session.
\end{Detail}

\BigGap
{\textbf{Anhui Provincial Hospital}}, Outpatient Unit, Psychiatric Department, Anhui, China

Volunteer/ Intern 
\hfill
Summer \DatestampY{2023}

\begin{Detail}
Involved in diagnostic assessments of, and pharmaceutical interventions for various mental, psychiatric, and neurological disorders in outpatient clinics with multiple medical professionals. 
\end{Detail}

\BigGap
\Entry
{\textbf{McGill Student Chinese Brush Arts Club}}

Vice President of Arts
\hfill
\DatestampYMD{2022}{09} -- Present

\begin{Detail}
\SubBulletItem
Teach Chinese calligraphy at weekly sessions.
\SubBulletItem
Represent the team and demonstrate calligraphy at various events.
\end{Detail}

%%%%%%%%%%%%%%%
%% LANGUAGES %%
%%%%%%%%%%%%%%%



%%%%%%%%%%%%
%% SKILLS %%
%%%%%%%%%%%%

\Section{Skills}
{Skills}
{PDF:Skills}

\Entry
{\textbf{Technical Skills}}

R, Python (beginner), {\LaTeX}, Microsoft CoPilot, Canva, Youtube.

\Gap

\Entry
{\textbf{Languages}}

English (fluent), Mandarin Chinese (native), French (intermediate; reading, speaking, writing).

\Section{Advanced Courses}
{Advanced Courses}
{PDF:Courses}
\Entry
Non-Parametric Statistics (MATH 524), Structural Equation Models (PSYC 531).

\end{Body}

\end{document}
